\vspace{-5em}\Huge Generation of a Synthetic Population and Travel Network for an Agent Based Traffic Simulation

### 2023-08-04 paper/paper.tex
paper labels are slightly different
slight update to paper

\quad Traffic modeling requires various inputs to accurately simulate a real world scenario. This paper takes a look at how to generate traffic demand for agent based models in particular. By taking a set of configurations from a user the proposed program stochastically produces a population as well as the network of a city. This data is then converted into a format that can be simulated and tested via simulation models. Thus, researchers can analyze the effect of various attributes of a road network on the traffic produced within it. With further modifications and enhancements, this software can also study the effects of different types of vehicles on carbon emissions. These improvements, as well as furthering multi-modal transportation are also discussed in this paper.

@@

\begin{multicols}{2}
    \section{Introduction}
    \quad Although agent based modeling has become increasingly popular in recent years, traffic simulations have existed for much longer. Previously, aggregate based four step models were the primary tool utilized. These systems did not capture the emergent effects of interactions between agents, and many did not even analyze the diversity of activities in each individual's schedules \cite{types-of-modeling}. Intuitively, this leads to several problems. First off, the lack of specific detail taken into account by these models results in simulations that simply predict patterns of groups of people. Multi-modal transportation is not captured very well in these cases. In addition, these models also don't work well with the variety of activities of different people in a population, thus they are limited by aggregate data as a whole. \\

    \quad Fortunately, nowadays, traffic simulation has started to move in the direction of agent based models \cite{ile-de-france}. These models function on a lower level, looking at the activities of people and their interactions \cite{agent-based-model}. However, in order to compute such specific predictions about a population, a lot of input data is required. Similar to any form of a simulation, you can't create information, just analyze it. Thus, the accuracy of the traffic demand determines the accuracy of the output. The best way to go about solving this problem is by sampling large populations down to an accurate, but still computable size. Still, very few governments openly release so much data about their populations. One example, can be seen in France, where an open source pipeline was created for this exact scenario of sampling \cite{ile-de-france}. The pipeline uses stochastic\footnote{Use of random probability to determine a quantity} models, such as the Monte Carlo simulation to sample an even size of the data of the France. In their case, the model results in data that is just 5\% of the size of Île-de-France's population. Having such a tool allows researchers to analyze existing traffic flows through agent based simulations, such as MATSIM\footnote{Open source framework for implementing agent based transport simulations} \cite{matsim}.\\

    \quad The pipeline above is one of many tools used to apply agent based modeling to real world scenarios. However, such methods do not allow for the analysis of hypothetical scenarios, such as variations in zoning policies. To do so, data must be manipulated and rely on the structure of a theoretical city. Unfortunately, such a program is not heavily invested in. In fact, prior to the publication of this paper, very few open source tools could generate a city structure based on simple and easy to use configurations. Therefore, the program discussed here was created to solve this problem. Broadly speaking, it is simply a tool to generate traffic demand. More specifically, however, this program is intended to allow researchers and city engineers to get a general understanding of how zoning policies, network layouts, and infrastructure of transport affect the cost of construction and traffic produced within the network as a whole. To understand the functionality and structure of this program, a clear explanation of simple city structure philosophies and general graph theory will be analyzed in this paper. This will be followed by an analysis of the algorithm's implementation. Finally, we will conclude with the actual simulation and possible improvements to this model in the future.

    \section{Theory}
    \quad As stated previously, the generation of traffic demand depends on a couple of very crucial background topics. Zoning policies are very important, as they are the center of how many cities around the world are designed. This program allows for euclidean zoning types of both hierarchical and flat zoning. The specifics of what these mean will be analyzed later, but in general both policies are very rigid. In fact, various papers link these types of zoning policies to urban sprawl \cite{zoning}. Though various other forms of zoning policies exist, euclidean zoning is by far the most popular and easy to implement.\\

    \quad Another topic that is very important to understand is graph theory. Having knowledge on basic graph theory will allow for a deeper intuition of how road networks are created. To allow for the configuration of the roads, a minimum spanning tree is used to create a base line infrastructure. On top of that, the networks contain meshed roads which are also subsets of the complete graph. More information will once again be analyzed, but this is one crucial implementation of Kruskal's algorithm\footnote{Algorithm to find the minimum spanning tree of a graph} in this paper. Another important use of graph theory on this project was its use for creating districts of cells in the zoning map. Rather than creating zones of all the same size, depth first search allowed the program to make cells of a grid interconnected for more realistic zones. Once again, this will be further covered in the city zoning section, but it is a general overview of how the following theories will be applied.

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.45\textwidth]{images/finalzoningwnodes.png}
        \caption{Final iteration of the nodes}
        \label{fig:first-zoning}
    \end{figure}

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.45\textwidth]{images/finalnetwork.png}
        \caption{Final iteration of the network}
        \label{fig:first-zoning}
    \end{figure}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.45\textwidth]{images/meshednetwork.png}
        \caption{Final iteration of the network with a 1\% meshing ratio}
        \label{fig:first-zoning}
    \end{figure}

>>>>

\quad Traffic modeling requires various inputs to accurately simulate a real world scenario. This paper takes a look at how to generate traffic demand for agent based models in particular. By taking a set of configurations from a user, the proposed program stochastically produces a population as well as the network of a city. This data is then converted into a format that can be simulated and tested via agent-based models. Thus, researchers can analyze the effect of various attributes of a road network on the traffic produced within it. With further modifications and enhancements, this software can also study the effects of different types of vehicles on carbon emissions. These improvements, as well as furthering multi-modal transportation are also discussed in this paper.

@@

\begin{multicols}{2}
    \section{Introduction}
    \quad Although agent-based modeling has become increasingly popular in recent years, traffic simulations have existed for much longer. Previously, aggregate four-step models were the primary tool utilized. These systems did not capture the emergent effects of interactions between agents, and many did not even analyze the diversity of activities in each individual's schedules \cite{types-of-modeling}. Intuitively, this leads to several problems. First off, the lack of specific detail taken into account by these models results in simulations that simply predict patterns of groups of people. Multi-modal transportation is not captured very well in these cases. In addition, these models also don't work well with the variety of activities of different people in a population, thus they are limited by aggregate data as a whole. \\

    \quad Fortunately, nowadays, traffic simulation has started to move in the direction of agent based models \cite{ile-de-france}. These models function on a lower level, looking at the activities of people and their interactions \cite{agent-based-model}. However, in order to compute such specific predictions about a population, a lot of input data is required. Similar to any form of a simulation, you can't create information, just analyze it. Thus, the accuracy of the traffic demand determines the accuracy of the output. The best way to go about solving this problem is by sampling large populations down to an accurate, but still computable size. Still, very few governments openly release sufficient data about their populations for traffic modeling. One example, can be seen in France, where an open-source pipeline was created for this exact scenario of sampling \cite{ile-de-france}. The pipeline uses stochastic\footnote{Use of random probability to determine a quantity} models, such as the Monte Carlo simulation to sample an even size of the data of the France. In their case, the model results in data that is just 5\% of the size of Île-de-France's population. Having such a tool allows researchers to analyze existing traffic flows through agent based simulations, such as MATSIM\footnote{Open source framework for implementing agent based transport simulations} \cite{matsim}.\\

    \quad The pipeline above is one of many tools used to apply agent-based modeling to real-world scenarios. However, such methods do not allow for the analysis of hypothetical scenarios, such as variations in zoning policies. To do so, data must be manipulated and rely on the structure of a theoretical city. Unfortunately, such a program does not readily exist. In fact, prior to the publication of this paper, very few open source tools could even generate a city structure based on real-world data. Therefore, the program discussed here was created to solve this problem. Broadly speaking, it is simply a tool to generate transportation networks and traffic demand. More specifically, however, this program is intended to allow researchers and city engineers to get a general understanding of how zoning policies, network layouts, and infrastructure of transport affect the cost of construction and traffic produced within the network as a whole. To understand the functionality and structure of this program, a clear explanation of simple city structure philosophies and general graph theory will be analyzed in this paper. This will be followed by an analysis of the algorithm's implementation. Finally, we will conclude with the actual simulation and possible improvements to this model in the future.

    \section{Theory}
    \quad As stated previously, the generation of traffic demand depends on a couple of very crucial background topics. Zoning policies are very important, as they are the center of how many cities around the world are designed. This program allows for Euclidean zoning types with both hierarchical and flat zoning. The specifics of what these mean will be analyzed later, but in general both policies are very rigid. In fact, various papers link these types of zoning policies to urban sprawl \cite{zoning}. Though various other forms of zoning policies exist, euclidean zoning is by far the most popular and easy to implement.\\

    \quad Another topic that is very important to understand is graph theory. Having knowledge on basic graph theory will allow for a deeper intuition of how road networks are created. To allow for the configuration of the roads, a minimum spanning tree is used to create a base line infrastructure. On top of that, the networks contain meshed roads which are also subsets of the complete graph. More information will once again be analyzed, but this is one crucial implementation of Kruskal's algorithm\footnote{Algorithm to find the minimum spanning tree of a graph} in this paper. Another important use of graph theory on this project was its use for creating districts of cells in the zoning map. Rather than creating zones of all the same size, depth-first search allowed the program to make cells of a grid interconnected for more realistic zones. Once again, this will be further covered in the city zoning section, but it is a general overview of how the following theories will be applied.

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.45\textwidth]{images/finalzoningwnodes.png}
        \caption{Final iteration of the nodes}
        \label{fig:final-zoning-nodes}
    \end{figure}

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.45\textwidth]{images/finalnetwork.png}
        \caption{Final iteration of the network}
        \label{fig:final-network}
    \end{figure}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.45\textwidth]{images/meshednetwork.png}
        \caption{Final iteration of the network with a 1\% meshing ratio}
        \label{fig:final-meshed-network}
    \end{figure}
